### 2017-06-23 src/4_OnlineLearning.tex
Avance hasta Competitive analysis

One example of regularisation in linear models is Ridge Regression (RR), which is a regularised least squares method.
The least squares (LS) method is a well known way to solve a regression
problem. 
LS method consists of minimising the sum of squared errors:

@@

@@

@@

In batch learning, the training phase is commonly a computationally expensive
process. Therefore, when new data arrives it can't be included easily to the
model. Moreover, it could happen that we won't have enough time to process the
new data before more data arrives. In online learning algorithms there is no
training phase, but the model is updated and evaluated at every time step. This
model updating is computationally less expensive than a training phase.
Online algorithms allow incremental learning by processing one instance at a
time. This is done updating the current model instead of building the model from
scratch.

@@

The online learning framework was first introduced in the perceptron algorithm
\cite{rosenblatt58}. There are several other widely used online methods such as
passive-aggressive \cite{crammerETall2006}, stochastic gradient descent
\cite{zhang2004}, aggregating algorithm \cite{vovk2001} and the second order
perceptron \cite{cesa-bianchi2005}.  In \cite{cesa-bianchi2006} an in-depth
analysis of online learning is provided.

@@

@@

Despite the bias-variance tradeoff provides a conceptual framework for
determining a good model, is not directly useful. Some popular methods
for determine model selection are:

\begin{itemize}
    \item Akaike information criterion (AIC) (Akaike, 1974)
    \item Bootstrap-based selection (Efron and Tibshirani, 1997)
    \item Cross-validation (Stone, 1974)
\end{itemize}

On the other hand, $\lambda$ can also be used to reduce computational time as it
is shown in equation~(\ref{eq:taylor}). Golub (~\cite{golub1965}) suggested that
$\lambda$ be chosen so that:

\[
\frac{\lambda}{\lambda + \delta^2} < 0.1
\]

\noindent where $\delta$ is a lower bound of the smallest non-zero singular
value $\sigma_k$. One approach is to choose the greatest lower bound for
$\delta=\sigma_k$. Hence:

\[
\frac{\lambda}{\lambda + \sigma_k^2} < 0.1
\]

\noindent if we choose $\lambda=\beta \sigma_k^2$ then we get the following
relation:

\[
\frac{\beta \sigma_k^2}{\beta \sigma_k^2 + \sigma_k^2} =
\frac{\beta}{\beta+1} < 0.1 \Rightarrow \beta < \frac{1}{9}  
\]

Experiments done by ~\cite{coleman+sun2010} have shown that $\beta = 0.01$
produces satisfactory results. This means that $\lambda = 0.01 \sigma_k^2$.

However, get $\sigma_k$ imply obtaining first the SVD, which is
computational expensive.

Since the algorithm presented by ~\cite{coleman+sun2010} already compute the QR
factorization of the matrix $\mathbf{A}$ they show a procedure for getting
a $\lambda$ approximation using QR.

\begin{enumerate}
\item Compute QR factorization: $\mathbf{A} = \mathbf{Q_1R_1}$
\item Let $\mathbf{W}$ denote the set of absolute values of the nonzero diagonal
elements of $\mathbf{R_1}$. Let $w_{\text{min}}$ and $w_{\text{max}}$ denote the
smallest and largest elements of $\mathbf{W}$ respectively. Both 
$\lambda_1 = \hat{\beta} w_{\text{min}}^2$
$\lambda_2 = \hat{\beta} \frac{w_{\text{min}}^2}{w_{\text{max}}^2}$ where
$\hat{\beta}=0.00025$ produce satisfactory results.
\item The $\lambda_{\text{QR}}$ approximation is obtained as:
$\lambda_{\text{QR}} = \frac{\lambda_1 + \lambda_2}{2}$  
\end{enumerate}

>>>>

Ridge regression was independently proposed by Tikhonov \cite{tikhonov1963} and Phillips \cite{phillips1962}. 
One example of regularisation in linear models is Ridge Regression (RR), which is a regularised least squares method.
The least squares (LS) method is a well known way to solve a regression
problem. 
LS method consists of minimising the sum of squared errors:

@@

The method is called ridge regression because the term $\lambda \mathbb{I}$ adds positive entries along the diagonal (ridge) to avoid the
singularity of the covariance matrix $\mathbf{A}^\top \mathbf{A}$. This addition ensures that all of the covariance matrix eigenvalues will be strictly greater than 0, i.e the solution becomes unique.

@@

\subsection{Generalized Cross Validation}
Since we don't know the data we want to predict, the bias-variance tradeoff is not directly useful to determine $\lambda$. Many techniques have been developed to determine a suitable value for the regularization parameter. However, when no information is available on the error, one of the most popular techniques is the Generalized Cross Validation (GCV) \cite{bauer2011}. 
GCV originates from the older method leave-one-out Cross Validation \cite{stone1974}.

The leave-one-out cross validation method determine a regularization parameter that minimises the average of the squared predictions errors using each solution to predict the missing data value.

%'---------------------------http://robjhyndman.com/hyndsight/crossvalidation/
%When the data are not independent cross-validation becomes more difficult as leaving out an observation does not remove all the associated information due to the correlations with other observations.

For time series forecasting, a cross-validation statistic is obtained as follows: fit the model to the data $y1,…,yt$ and let $y^t+1$ denote the forecast of the next observation. Then compute the error ($et+1∗=yt+1−y^t+1$) for the forecast observation.
Repeat step 1 for t=m,…,n−1 where m is the minimum number of observations needed for fitting the model.
Compute the MSE from $em+1∗,…,en∗$.

%An excellent and comprehensive recent survey of cross-validation results is Arlot and Celisse (2010)

%---------------------------------------------------

@@

In batch learning, the training phase is commonly a computationally expensive
process. Therefore, when new data arrives it can't be included easily to the
model. Moreover, it could happen that we won't have enough time to process the
new data before more data arrives. In online learning algorithms there is no
training phase, but the model is updated and evaluated at every time step. This
model updating is computationally less expensive than a training phase.

Online algorithms allow incremental learning by processing one instance at a
time. This is done updating the current model instead of building the model from
scratch.

@@

The online learning framework was first introduced in the perceptron algorithm
\cite{rosenblatt58}. There are several other widely used online methods such as
passive-aggressive \cite{crammerETall2006}, stochastic gradient descent
\cite{zhang2004}, aggregating algorithm \cite{vovk2001} and the second order
perceptron \cite{cesa-bianchi2005}.  In \cite{cesa-bianchi2006} an in-depth
analysis of online learning is provided. Applications in finance has been widely used: study presented by~\cite{arce+salinas2012} applied ridge regression in an online context and more recently, time series forecasting using online learning has been presented~\cite{anavaetAl2013}.

@@

%REVISADO HASTA ACA

@@

%Despite the bias-variance tradeoff provides a conceptual framework for
%determining a good model, is not directly useful. Some popular methods
%for determine model selection are:
%
%\begin{itemize}
%    \item Akaike information criterion (AIC) (Akaike, 1974)
%    \item Bootstrap-based selection (Efron and Tibshirani, 1997)
%    \item Cross-validation (Stone, 1974)
%\end{itemize}
%
%On the other hand, $\lambda$ can also be used to reduce computational time as it
%is shown in equation~(\ref{eq:taylor}). Golub (~\cite{golub1965}) suggested that
%$\lambda$ be chosen so that:
%
%\[
%\frac{\lambda}{\lambda + \delta^2} < 0.1
%\]
%
%\noindent where $\delta$ is a lower bound of the smallest non-zero singular
%value $\sigma_k$. One approach is to choose the greatest lower bound for
%$\delta=\sigma_k$. Hence:
%
%\[
%\frac{\lambda}{\lambda + \sigma_k^2} < 0.1
%\]
%
%\noindent if we choose $\lambda=\beta \sigma_k^2$ then we get the following
%relation:
%
%
%\[
%\frac{\beta \sigma_k^2}{\beta \sigma_k^2 + \sigma_k^2} =
%\frac{\beta}{\beta+1} < 0.1 \Rightarrow \beta < \frac{1}{9}  
%\]
%
%Experiments done by ~\cite{coleman+sun2010} have shown that $\beta = 0.01$
%produces satisfactory results. This means that $\lambda = 0.01 \sigma_k^2$.
%
%However, get $\sigma_k$ imply obtaining first the SVD, which is
%computational expensive.
%
%Since the algorithm presented by ~\cite{coleman+sun2010} already compute the QR
%factorization of the matrix $\mathbf{A}$ they show a procedure for getting
%a $\lambda$ approximation using QR.
%
%\begin{enumerate}
%\item Compute QR factorization: $\mathbf{A} = \mathbf{Q_1R_1}$
%\item Let $\mathbf{W}$ denote the set of absolute values of the nonzero diagonal
%elements of $\mathbf{R_1}$. Let $w_{\text{min}}$ and $w_{\text{max}}$ denote the
%smallest and largest elements of $\mathbf{W}$ respectively. Both 
%$\lambda_1 = \hat{\beta} w_{\text{min}}^2$
%$\lambda_2 = \hat{\beta} \frac{w_{\text{min}}^2}{w_{\text{max}}^2}$ where
%$\hat{\beta}=0.00025$ produce satisfactory results.
%\item The $\lambda_{\text{QR}}$ approximation is obtained as:
%$\lambda_{\text{QR}} = \frac{\lambda_1 + \lambda_2}{2}$  
%\end{enumerate}
